Revealing Transient Strain in Geodetic Data with the Radial Basis Function Finite Difference Method

### 2017-06-12 HinesHetlandGPR.tex
added more

As another test to determine the most appropriate covariance function for $T$, we compare the observations to the predicted displacements for each covariance function. let $\hat{\bm{d}} = \left(u(\bm{y}) + \bm{P}\bm{a}\right)|\bm{d}_*$ be the data prediction vector. It can be shown that $\bm{d}_*$ is normally distributed with mean 
\begin{equation}\label{eq:DataPredMean}
\bm{\mu}_{\hat{d}} =
\left[ 
\begin{array}{cc}
C_u(\bm{y},\bm{y}) & \bm{P} \\
\end{array}
\right]
\left[
\begin{array}{cc}
\bm{\Sigma} & \bm{P} \\
\bm{P}^T  & \bm{0} \\
\end{array}
\right]^{-1}
\left[
\begin{array}{c}
\bm{d}_* \\
\bm{0} \\
\end{array}
\right]
\end{equation}  
and covariance
\begin{equation}\label{eq:DataPredCov}
\bm{C}_{\hat{\bm{d}}} = 
C_u(\bm{y},\bm{y}) - 
\left[ 
\begin{array}{cc}
C_u(\bm{y},\bm{y}) & \bm{P} \\
\end{array}
\right]
\left[
\begin{array}{cc}
\bm{\Sigma} & \bm{P} \\
\bm{P}^T  & \bm{0} \\
\end{array}
\right]^{-1}
\left[
\begin{array}{c}
C_u(\bm{y},\bm{y}) \\
\bm{P}^T \\
\end{array}
\right].
\end{equation}
We compute $\hat{\bm{d}}$ using SE, Wendland, and IBM covariance functions for $T$ and the median hyperparameters from Table 1. Figure 1 compares the easting component of $\bm{d}_*$ to $\hat{\bm{d}}$ for the Winter 2016 SSE.  For most stations, the data prediction vector appears to appropriately describe displacements throughout the SSE, regardless of the choice of $T$. The prediction for the IBM model contains slightly more high frequency, and perhaps spurious, features. The predictions for the Wendland and SE covariance functions are nearly indistinguishable. We ultimately settle on the Wendland covariance function for $T$. We choose the Wendland covariance function over the SE covariance function because of its computational advantages noted above.

@@

@@

>>>>

As another test to determine the most appropriate covariance function for $T$, we compare the observations to the predicted displacements for each covariance function. let $\hat{\bm{d}} = \left(u(\bm{y}) + \bm{P}\bm{a}\right)|\bm{d}_*$ be the data prediction vector. It can be shown that $\hat{\bm{d}}$ is normally distributed with mean 
\begin{equation}\label{eq:DataPredMean}
\bm{\mu}_{\hat{d}} =
\left[ 
\begin{array}{cc}
C_u(\bm{y},\bm{y}) & \bm{P} \\
\end{array}
\right]
\left[
\begin{array}{cc}
\bm{\Sigma} & \bm{P} \\
\bm{P}^T  & \bm{0} \\
\end{array}
\right]^{-1}
\left[
\begin{array}{c}
\bm{d}_* \\
\bm{0} \\
\end{array}
\right]
\end{equation}  
and covariance
\begin{equation}\label{eq:DataPredCov}
\bm{C}_{\hat{\bm{d}}} = 
C_u(\bm{y},\bm{y}) - 
\left[ 
\begin{array}{cc}
C_u(\bm{y},\bm{y}) & \bm{P} \\
\end{array}
\right]
\left[
\begin{array}{cc}
\bm{\Sigma} & \bm{P} \\
\bm{P}^T  & \bm{0} \\
\end{array}
\right]^{-1}
\left[
\begin{array}{c}
C_u(\bm{y},\bm{y}) \\
\bm{P}^T \\
\end{array}
\right].
\end{equation}
We compute $\hat{\bm{d}}$ using SE, Wendland, and IBM covariance functions for $T$ and the median hyperparameters from Table 1. Figure 1 compares the easting component of $\bm{d}_*$ to $\hat{\bm{d}}$ for the Winter 2016 SSE.  For most stations, the data prediction vector appears to appropriately describe displacements throughout the SSE, regardless of the choice of $T$. The prediction for the IBM model contains slightly more high frequency, and perhaps spurious, features. The predictions for the Wendland and SE covariance functions are nearly indistinguishable. We ultimately settle on the Wendland covariance function for $T$. We choose the Wendland covariance function over the SE covariance function because of its computational advantages noted above.

\begin{figure*}
\includegraphics{figures/signal_fit/signal-fit.pdf}
\caption{Fit.}   
\label{fig:Fit}
\end{figure*}

@@

\begin{figure*}
\includegraphics{figures/strain_map/strain-map.pdf}
\caption{Strain map.}   
\label{fig:Fit}
\end{figure*}

@@

\begin{figure*}
\includegraphics{figures/strain_ts/strain-ts.pdf}
\caption{Strain time series.}   
\label{fig:Fit}
\end{figure*}

\begin{figure*}
\includegraphics{figures/strain_ts/mag-ts.pdf}
\caption{Strain magnitude time series.}   
\label{fig:Fit}
\end{figure*}

A video can be found as supp material
